A full approximation scheme multilevel method \\ for solving nonlinear variational inequalities

### 2024-07-23 talk-ismp/slides.tex
small improvements after 1st practice

\begin{itemize}
\item the VI gives an ``angle condition'' for the test function $v-u$:
\item in optimization problems the condition is a consequence:
\begin{align*}
J(u) &\le J(v) \quad \forall v \in \mathcal{K} \\
\implies \qquad \ip{J'(u)}{v-u} &\ge 0 \quad \forall v \in \mathcal{K}
\end{align*}
\item for general VIs the condition \emph{is} the problem:
   $$\ip{F(u)}{v-u} \ge 0 \quad \forall v \in \mathcal{K}$$    
\end{itemize}

\bigskip
\begin{center}
\includegraphics[width=0.4\textwidth]{../talk-dms/figs/convexuv.png}
\end{center}
\end{frame}

@@

\vspace{1.5mm}
\item<2> first-semester calculus:
    $$u = \mathop{\textnormal{argmin}}_{x\in[a,b]} f(x) \quad \iff \quad f'(u)(v-u) \ge 0 \quad \forall v \in[a,b]$$
\end{itemize}

\vspace{-5mm}
\begin{center}
\only<1>{\vspace{20.5mm}}

\includegraphics<2>[height=25mm]{../talk-oxford/images/calcone.png}
\end{center}
\end{frame}

@@

\begin{itemize}
\item FAS multigrid is a fast solver on nice nonlinear PDE problems
\item example: Liouville-Bratu equation
    $$-\nabla^2 u - e^u = 0$$
with Dirichlet boundary conditions on $\Omega=(0,1)^2$
\item minimal problem-specific code:
    \begin{enumerate}
    \item[1.] residual evaluation on grid level: $F^j(\cdot)$
    \item[2.] pointwise smoother: $\phi_i(c) = 0 \,\forall i$
        \begin{itemize}
        \item[$\circ$] nonlinear Gauss-Seidel iteration
        \end{itemize}
    \item[3.] coarsest-level solve can be same as smoother
    \end{enumerate}
\end{itemize}
\end{frame}

>>>>

\begin{itemize}
\item the VI gives an ``angle condition'' for the test function $v-u$
\item in optimization problems the VI is a consequence:
$$J(u) \le J(v), \, \forall v \in \mathcal{K} \qquad \implies \qquad \ip{J'(u)}{v-u} \ge 0, \, \forall v \in \mathcal{K}$$
\item for general VIs the angle condition \emph{is} the problem:
   $$\ip{F(u)}{v-u} \ge 0 \quad \forall v \in \mathcal{K}$$    
\end{itemize}

\bigskip
\begin{center}
\includegraphics[width=0.4\textwidth]{figs/convexuv.png}
\end{center}
\end{frame}

@@

\vspace{1.5mm}
\item first-semester calculus:
    $$u = \mathop{\textnormal{argmin}}_{x\in[a,b]} f(x) \quad \iff \quad f'(u)(v-u) \ge 0 \quad \forall v \in[a,b]$$
\end{itemize}

\vspace{-5mm}
\begin{center}
\includegraphics[height=25mm]{../talk-oxford/images/calcone.png}
\end{center}
\end{frame}

@@

\begin{itemize}
\item FAS multigrid is a fast solver on nice nonlinear PDE problems
\item example: Liouville-Bratu equation
    $$-\nabla^2 u - e^u = 0$$
with Dirichlet boundary conditions on $\Omega=(0,1)^2$
%\item minimal problem-specific code:
%    \begin{enumerate}
%    \item[1.] residual evaluation on grid level: $F^j(\cdot)$
%    \item[2.] pointwise smoother: $\phi_i(c) = 0 \,\forall i$
%        \begin{itemize}
%        \item[$\circ$] nonlinear Gauss-Seidel iteration
%        \end{itemize}
%    \item[3.] coarsest-level solve can be same as smoother
%    \end{enumerate}
\end{itemize}
\end{frame}
